\documentclass{article}

\title{Misguided by Starlight}
\author{Skoddie}

\usepackage{subfiles}

\begin{document}
\maketitle

\section{Books}
- World of Darkness
If you would like your character to have anything from another book, feel free to ask, understanding that you may be denied. Ultimately everything allowed in this campaign will be in this document.

\section{Attributes}

	\subfile{sections/Attributes}

\section{Skills}

	\subfile{sections/Skills}

\section{Skill Specialties}
You can buy the same specialty up to three times for a total +3 bonus when that specialty applies.

\section{Merits}

	\subfile{sections/Merits}

\section{Practical Skill Advancement}
When the game begins you will be given a Practical Skill Advancement Worksheet for recording successful and failed checks on skill rolls. When you have accumulated a number of successes and failures equal to your current skill level +1 you may gain a free dot in that skill.

\section{Noms}
At the end of each chapter and the GM may nominate a player for exemplary roleplay. These may be spent during play to reroll one failed die or lower the explode threshold on a single die.
Improving on 10-again
- Any effect which improves the 10-again mechanic behaves as follows:
\begin{itemize}
	\item Rolls without 10-again regain 10-again
	\item 10-again becomes 9-again
	\item 9-again becomes 8-again
	\item These effects stack
	\item No roll may be reduced below 8-again
\end{itemize}

\section{Experience}
- All traits have flat costs:
\begin{itemize}
	\item Attribute 15 exp
	\item PSA Point 3 exp
	\item Skill Specialty 3 exp
	\item Merit 6 exp
	\item Willpower 8 exp (restore spent dot)
\end{itemize}
- The fifth dot of a trait does not cost double at creation.

\end{document}