\documentclass["../Misguided by Starlight.tex"]{subfiles}

\begin{document}
% Sniper: One Shot, One Kill fighting style merit applies to aiming bonus instead of weapon rating.
% Fighting style merits which grant extra attacks use split dice pools instead of cumulative penalties.
% Fighting style merits may not be combined with offhand attacks or autofire unless stated.

The merits listed below are the only merits allowed in this campaign.

\subsection{Mental}
	\subsubsection{Common Sense ($\bullet$ $\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Effect:} Your character is exceptionally grounded and pragmatic, and can usually be depended upon to make sound, straightforward decisions after a few moments' thought.
		
		The Storyteller can make a reflexive Wits + Composure roll once per chapter for your character if he is about to embark on a disastrous course of action, or if you find yourself at a point in the story where you're completely stumped for ideas. If the roll succeeds, the Storyteller may point out the risks of a particular course, or suggest possible actions that your character can take that might get events back on track. N ote: While you're free to ask the Storyteller for a Common Sense roll when you're out of ideas, he is under no obligation to comply. It's an aid, not a crutch. \emph{Available at character creation only.}
		
	\subsubsection{Danger Sense ($\bullet$ $\bullet$)} %WoD
		\textbf{Effect:} You gain a +2 modifier on reflexive Wits + Composure rolls for your character to detect an impending ambush. This kind of roll is typically made prior to the first turn of a surprise attack. Your character has a well-developed survival instinct that warns him of impending danger. Perhaps he's adept at reading subtle clues in his environment or he possesses an uncanny ``sixth sense'' when it comes to avoiding trouble.
	
	\subsubsection{Eidetic Memory ($\bullet$ $\bullet$)} %WoD
		\textbf{Effect:} Your character has a near-photographic memory, being able to recall vast amounts of observed detail with astonishing accuracy. You do not normally need to make a roll for your character to remember an obscure fact or past experience, unless he is under stress (such as in combat). Under stress, there is a +2 modifier on any Intelligence + Composure or other Skill-based roll (say, Academics, to remember a fact) for memory recall. \emph{Available at character creation only.}
	\subsubsection{Good Time Management ($\bullet$)} %GM
	
	\subsubsection{Encyclopedic Knowledge ($\bullet$ $\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Effect:} Your character is a veritable font of useful (and sometimes useless) information on a wide variety of topics. Chances are he can come up with an anecdote pertaining to any situation based on something he's read, witnessed or seen on TV.
		
		You can make an Intelligence + Wits roll any time your character is confronted with a situation or phenomenon outside his normal realm of experience. If the roll is successful, he may recall a ``factoid'' that he's heard at some point that may shed light on matters.
		
		\emph{Available at character creation only.} Your character has either been soaking up trivia all his life or he hasn't.
		
		\textbf{Dramatic Failure:} Your character ``remembers'' something about the situation that is completely inaccurate.``ÒWait! Wait! I saw something like this in a movie once!'' The Storyteller might make Intelligence + Wits rolls on your behalf when a dramatic failure is possible.
		
		\textbf{Failure:} Your character wracks his brain but comes up empty.
		
		\textbf{Success:} Your character remembers a detail or fact that sheds some light on the situation. ``You said there was an almond odor? Seems to me I read somewhere that's a sign of cyanide poisoning.''
		
		\textbf{Exceptional Success:} Your character recalls a number of useful details that provide extensive insight. ``Hey, cool --- a little candy skull. They make these in Mexico for the Day of the Dead. It's an offering for a loved one who's died. And they say you can't learn anything on TV.''
	
	\subsubsection{Language ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$)} %Custom
		Each language a character learns is a separate merit. The dot value of the merit is based on the difficulty of the language for English speakers (see below). Language and Multi-Lingual merits may both be purchased multiple times.

		With the Language merit, a character can speak the language like a native and is well-read in it.

		Languages preceded by asterisks do not include literacy; the same merit must be purchased a second time at the same level to read and write that language.
		
		\begin{itemize}
			\item ($\bullet$) Closely related to English
			\begin{itemize}
				\item Afrikaans
				\item Catalan
				\item Danish
				\item Dutch
				\item Esperanto
				\item French
				\item Galician
				\item Italian
				\item Norwegian
				\item Portuguese
				\item Romanian
				\item Spanish
				\item Swedish
			\end{itemize}
				
			\item ($\bullet$ $\bullet$) Similar to English
			\begin{itemize}
				\item German
			\end{itemize}

			\item ($\bullet$ $\bullet$ $\bullet$ $\bullet$) Linguistic and/or cultural differences from English
			\begin{itemize}
				\item Indonesian
				\item Javanese
				\item Jumieka
				\item Malay
				\item Swahili
			\end{itemize}
		 
			\item ($\bullet$ $\bullet$ $\bullet$ $\bullet$) Significant linguistic and/or cultural differences from English
			\begin{itemize}
				\item Albanian
				\item Amharic
				\item Armenian
				\item Azerbaijani
				\item Belarusian
				\item Bengali
				\item Bosnian
				\item Bulgarian
				\item Burmese
				\item Cebuano
				\item Croatian
				\item Czech
				\item *Dzongkha
				\item *Estonian
				\item *Finnish
				\item *Georgian
				\item Greek
				\item Gujarati
				\item Hebrew
				\item Hindi
				\item *Hungarian
				\item Icelandic
				\item Ilocano
				\item Irish
				\item Kannada
				\item Kazakh
				\item Kurdish
				\item Kyrgyz
				\item Khmer
				\item Lao
				\item Latin
				\item Latvian
				\item Lithuanian
				\item Macedonian
				\item Marathi
				\item *Mongolian
				\item Nepali
				\item Pashto
				\item Persian (Dari, Farsi, Tajik)
				\item Polish
				\item Punjabi
				\item Russian
				\item Serbian
				\item Sinhalese
				\item Slovak
				\item Slovenian
				\item Somali
				\item Tagalog
				\item Tamil
				\item Telugu
				\item Tetum
				\item *Thai
				\item Turkish
				\item Turkmen
				\item Ukrainian
				\item Urdu
				\item Uzbek
				\item *Vietnamese
				\item Xhosa
				\item Zulu
			\end{itemize}

			\item ($\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$) Exceptionally difficult for native English speakers
			\begin{itemize}
				\item Arabic
				\item Cantonese (Chinese)
				\item *Japanese
				\item Korean
				\item Mandarin (Chinese)
				\item Taiwanese (Hokkien Min Nan)
				\item Wu
			\end{itemize}
		\end{itemize}
	
	\subsubsection{Meditative Mind ($\bullet$, $\bullet$ $\bullet$, or $\bullet$ $\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Effect:} Your character’s meditation is far more fulfilling than for other characters. With the one-dot version of this Merit, the character does not suffer environment penalties to meditation (see the \textbf{World of Darkness Rulebook, p. 51}), even from wound penalties.
		
		With the two-dot version, when the character has successfully meditated, she gains a +3 bonus on any Resolve + Composure rolls during the same day as she’s steeled herself against the things of the world that would shake her foundation.

		At the four-dot level, she only needs a single success to gain the benefits of meditation for the day, instead of the normal four.
	
	\subsubsection{Multi-Lingual ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$)} %Custom
		With the Multi-Lingual merit, a character can read, write, and speak multiple languages with basic fluency. The Multi-Lingual merit rating is equal to the most difficult language the player wishes to include and grants double its dot rating in language dots, divided however the player sees fit among equal or lower ranked languages.
		
	\subsubsection{Patient ($\bullet$)} %GM
		\textbf{Effect:} Your character knows how to pace herself and take the time to do the job right the first time. When taking an extended action, you may make two additional rolls above what your Attribute + Skill would allow.
	
	\subsubsection{Professional Training ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Effect:} Your character has extensive training in a particular profession, which offers distinct advantages in a handful of fields. When choosing this Merit, choose or create a Profession for your character (see the sidebar). Mark the two Asset Skills on your character sheet. The advantages of Professional Training relate directly to those Asset Skills.
		
			\begin{itemize}
				\item $\bullet$ Networking: At the first level of Professional Training, your character builds connections within her chosen field. Take two dots of Contacts relating to that field.
				
				\item $\bullet$ $\bullet$ Continuing Education: With repeated efforts in her field of choice, your character tends toward greater successes. When making a roll with her Asset Skills, she benefits from the 9-again quality.
				
				\item $\bullet$ $\bullet$ $\bullet$ Breadth of Knowledge: Due to advancement in her field, she’s picked up a number of particular bits of information and skill unique to her work. Choose a third Asset Skill and take two Specialties in your character’s Asset Skills.
				
				\item $\bullet$ $\bullet$ $\bullet$ $\bullet$ On the Job Training: With the resources at her disposal, your character has access to extensive educational tools and mentorship available. Take a Skill dot in an Asset Skill. Whenever you purchase a new Asset Skill dot, take a Beat.
				
				\item $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$ The Routine: With such extensive experience in her field, her Asset Skills have been honed to a fine edge and she’s almost guaranteed at least a marginal success. Before rolling, spend a Willpower point to apply the rote action quality to an Asset Skill. This allows you to reroll all the failed dice on the first roll.
			\end{itemize}
			
	
	\subsubsection{Tolerance for Biology ($\bullet$)} %GM
		\textbf{Prerequisite:} Resolve $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Most people turn away at the sight of blood, other bodily fluids, or exotic biology. Your character has seen enough that nothing turns her stomach. When other characters must resist shock or physical repulsion from the disgusting and morbid, your character stands her ground. You do not need to make Composure, Stamina, or Resolve rolls to withstand the biologically strange. This doesn’t mean she’s immune to fear; she’s just used to nature in all its nasty forms.
	
	\subsubsection{Trained Observer ($\bullet$ or $\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Wits $\bullet$ $\bullet$ $\bullet$ or Composure $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character has spent years in the field, catching tiny details and digging for secrets. She might not have a better chance of finding things, but she has a better chance of finding important things. Any time you make a Perception roll (usually Wits + Composure), you benefit from the 9-again quality. With the three-dot version, you get 8-again.
	
\subsection{Physical}
	\subsubsection{Ambidextrous ($\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Effect:} Your character does not suffer the -2 penalty for using his off-hand in combat or to perform other actions. \emph{Available at character creation only.}
	
	\subsubsection{Demolisher ($\bullet$ to $\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Strength $\bullet$ $\bullet$ $\bullet$ or Intelligence $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character has an innate feel for the weak points in objects. When damaging an object, she ignores one point of the object’s Durability per dot in this Merit.
	
	\subsubsection{Direction Sense ($\bullet$)} %WoD
		\textbf{Effect:} Your character has an innate sense of direction that instinctively allows him to remain oriented. He can enter unfamiliar territory and always retrace his steps back to his starting point, and can orient himself to any of the compass points (i.e., face north, face south) without references.
	
	\subsubsection{Double Jointed ($\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Dexterity $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character might have been a contortionist or spent time practicing yoga. She can dislodge joints when need be. She automatically escapes from any mundane bonds without a roll. When grappled, subtract her Dexterity from any rolls to overpower her as long as she’s not taking any aggressive actions.
	
	\subsubsection{Fast Reflexes ($\bullet$ or $\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Wits $\bullet$ $\bullet$ $\bullet$ or Dexterity $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character’s reflexes impress and astound; she’s always fast to react. +1 Initiative per dot.
	
	\subsubsection{Fleet of Foot ($\bullet$ to $\bullet$ $\bullet$ $\bullet$)} %WoD
		 \textbf{Prerequisite:} Strength $\bullet$ $\bullet$
		 
		 \textbf{Effect:}  +1 Speed per dot 
		 	
		Regardless of your character’s physical build, he can run quickly when he chooses to.
	
	\subsubsection{Giant ($\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Effect:} Your character is massive. She’s well over six feet tall and crowds part when she approaches. She’s Size 6 and gains +1 Health. \emph{Available only at character creation.}
		
		\textbf{Drawback:} Buying clothing is a nightmare. Fitting in small spaces is difficult at best.
	
	\subsubsection{Hardy ($\bullet$ to $\bullet$ $\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:}  Stamina $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character’s body goes further than it rightfully should. Add the dots in this Merit to any rolls to resist disease, poison, deprivation, unconsciousness, or suffocation.
	
	\subsubsection{Iron Stamina ($\bullet$ to $\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Prerequisite:} Stamina $\bullet$ $\bullet$ $\bullet$ or Resolve $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Each dot eliminates a negative modifier (on a one-for-one basis) when resisting the effects of fatigue or injury. For example: A character with Iron Stamina $\bullet$ $\bullet$ is able to ignore up to a -2 modifier brought on by fatigue. See “Fatigue,” p. 179. The Merit also counteracts the effects of wound penalties. So, if all of your character’s Health boxes are filled (which normally imposes a -3 penalty to his actions) and he has Iron Stamina $\bullet$, those penalties are reduced to -2. This Merit cannot be used to gain positive modifiers for actions, only to cancel out negative ones.
		
		Your character can push his body well past the limits of physical endurance when he has to, pressing on in the face of mounting exhaustion or pain. Perhaps he trained himself to go without sleep for days at a time in order to get through college, or a lifetime of sports has taught your character how to play through the pain no matter how bad it gets.
		
		\textbf{Drawback:} When your character does finally rest, he sleeps like the dead. After staying awake for an extended period, your character is extremely difficult to wake until he’s slept for a minimum of 12 hours, regardless of the situation.
	
	\subsubsection{Iron Stomach ($\bullet$ $\bullet$)} %WoD
		\textbf{Prerequisite:} Stamina $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character can eat almost anything, under almost any conditions. Greasy bacon and runny eggs on a raging hangover? No problem. The green meat in the fridge? No problem. Milk two weeks past its expiration date? No problem. He could be dropped in the middle of the forest and could live off bugs and roots as long as necessary in order to survive — and with no ill effects. Add two dice to appropriate Survival rolls. Add three to Stamina to resist deprivation (see p. 175).
	
	\subsubsection{Natural Immunity ($\bullet$)} %WoD
		\textbf{Prerequisite:} Stamina $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character gains a +2 modifier on Stamina rolls to resist infection, sickness and disease. His immune system is exceptionally effective at resisting infections, viruses and bacteria. Your character can probably count on one hand the number of times he’s been seriously ill.
	
	\subsubsection{Quick Draw ($\bullet$)} %GM
		\textbf{Prerequisite:} Wits $\bullet$ $\bullet$ $\bullet$, a Specialty in the weapon or fighting style chosen.
		
		\textbf{Effect:} Choose a Specialty in Weaponry or Firearms when you purchase this Merit. Your character has trained enough in that weapon or style that pulling the weapon is her first reflex. Drawing or holstering that weapon is considered a reflexive action, and can be done any time her Defense applies.
	
	\subsubsection{Quick Healer ($\bullet$ $\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Prerequisite:} Stamina $\bullet$ $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:}Your character’s healing abilities are remarkable, allowing him to bounce back quickly from injuries that would leave most people bedridden for months. 
		
		Your character recovers from injuries in half the time that others do. One point of bashing damage is healed in eight minutes. One point of lethal damage is healed in one day. One point of aggravated damage is healed in four days.
	
	\subsubsection{Sleight of Hand ($\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Larceny $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character can pick locks and pockets without even thinking about it. She can take one Larceny-based instant action reflexively in a given turn. As well, her Larceny actions go unnoticed unless someone is trying specifically to catch her.
	
	\subsubsection{Small Framed ($\bullet$ $\bullet$)} %GM
		\textbf{Effect:} Your character is diminutive. She’s not even five feet tall and it’s easy to walk into her without noticing. She’s Size 4 and thus has one fewer Health box. She gains +2 to any rolls to hide or go unnoticed. This bonus might apply any time being smaller would be an advantage, such as crawling through smaller spaces. \emph{Available only at character creation.} 
		
		\textbf{Drawback:} In addition to the lower Health, your character might be overlooked or not taken seriously by some people.
	
	\subsubsection{Strong Back ($\bullet$)} %WoD
		\textbf{Prerequisite:} Strength $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character gains a +1 modifier to actions involving lifting or carrying heavy weights. She can lift and carry much more weight than her build and body type suggests.
	
	\subsubsection{Strong Lungs ($\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Prerequisite:} Athletics $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character is practiced at holding his breath for long periods of time. He might be a pearl diver or escape artist, capable of staying underwater without aid for longer than most people believe is possible. 
		
		When determining how long your character can hold his breath, add two to Stamina when referencing the Holding Breath chart on p. 49. For example, if your character’s Stamina is 2, he can hold his breath for four minutes before you need to make a roll.
	
\subsection{Social}
	\subsubsection{Barfly ($\bullet$)} %WoD
		\textbf{Effect:} No matter what town or city your character is in, he can find his way into the best nightspots with a few quick words and a timely bribe. There isn’t a velvet rope made that can keep him out of a restaurant or club.
	
	\subsubsection{Inspiring ($\bullet$ $\bullet$ $\bullet$ $\bullet$)} %WoD
		\textbf{Prerequisite:} Presence $\bullet$ $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character is able to rally others in times of great distress, renewing their courage and determination in the face of adversity. Once per game session, your character can exhort those around him to redouble their efforts in the face of great stress or danger. Make a Presence + Persuasion roll. If the roll succeeds, any individuals who actively assist your character and who are within earshot regain one spent Willpower point (not to exceed their Willpower dots). The character may not use this Merit on himself, and may not use it on the same subjects more than once a day
	
	\subsubsection{Iron Will ($\bullet$ $\bullet$)} %GM
		\textbf{Prerequisite:} Resolve  $\bullet$ $\bullet$ $\bullet$ $\bullet$
		
		\textbf{Effect:} Your character’s resolve is unwavering. When spending Willpower to contest or resist in a Social interaction, you may substitute your character’s Resolve for the usual Willpower bonus. If the roll is contested, roll with 8-again.
	
	\subsubsection{Striking Looks ($\bullet$ or $\bullet$ $\bullet$)} %GM
		\textbf{Effect:} Your character is stunning, alarming, commanding, repulsing, threatening, charming, or otherwise worthy of attention. Determine how your character looks and how people react to that. For one dot, your character gets a +1 bonus on any Social rolls that would be influenced by her looks. For two dots, the benefit increases to +2. Depending on the particulars, this might influence Expression, Intimidation, Persuasion, Subterfuge, or other rolls. 
		
		\textbf{Drawback:} Attention is a double-edged sword. Any rolls to spot, notice, or remember your character gain the same die bonus. Sometimes, your character will draw unwanted attention in social situations. This could cause further complications.
	
\subsection{Fighting Merits} %All are GM
	\subsubsection{Armed Defense ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Cheap Shot ($\bullet$ $\bullet$)} %GM
	
	\subsubsection{Choke Hold ($\bullet$ $\bullet$)} %GM
	
	\subsubsection{Close Quarters Combat ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Defensive Combat ($\bullet$)} %GM
	
	\subsubsection{Fighting Finesse ($\bullet$ $\bullet$)} %GM
	
	\subsubsection{Firefight ($\bullet$ to $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Grappling ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Improvised Weaponry ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Iron Skin ($\bullet$ $\bullet$ or $\bullet$ $\bullet$ $\bullet$ $\bullet$)} %GM
	
	\subsubsection{Light Weapons ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Martial Arts ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Shiv ($\bullet$ or $\bullet$ $\bullet$)} %GM
	
	\subsubsection{Street Fighting ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM
	
	\subsubsection{Unarmed Defense ($\bullet$ to $\bullet$ $\bullet$ $\bullet$ $\bullet$ $\bullet$; Style)} %GM

\end{document}
